---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# simcdm 

[![Build Status](https://travis-ci.org/tmsalab/simcdm.svg)](https://travis-ci.org/tmsalab/simcdm)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN](http://www.r-pkg.org/badges/version/simcdm)](https://cran.r-project.org/package=simcdm)
[![Downloads](http://cranlogs.r-pkg.org/badges/simcdm?color=brightgreen)](http://www.r-pkg.org/pkg/simcdm)
[![Coverage status](https://codecov.io/gh/tmsalab/simcdm/branch/master/graph/badge.svg)](https://codecov.io/github/tmsalab/simcdm?branch=master)

The goal of `simcdm` is to provide flexible ways to simulate data under
cognitive diagnostic models.

## Installation

You can install simcdm from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tmsalab/simcdm")
```

## Usage

To use `simcdm`, load the package using:

```{r example}
library("simcdm")
```

## Overview

There are three distinct sets of functions within the package:

- Attributes: `attribute_classes()`, `attribute_bijection()`, `attribute_inv_bijection()`, and `sim_subject_attributes()`.
- Matrix: `sim_q_matrix()` and `sim_eta_matrix()`
- Deterministic Input, Noisy And Gate (DINA): `sim_dina_items()` and `sim_dina_attributes()`
- reduced Reparameterized Unified Model (rRUM): `sim_rrum_items()`

Functions that use random numbers to simulate values are named with the prefix of
`sim_*()`. This is done to allow for functions to be quickly identified and used
through autocomplete inside of the [RStudio IDE](https://www.rstudio.com). At
a later time, the `attribute_*()` will likely be moved to a different package.

For more details, please see the [package vignettes](vignettes/):

- [Overview of `simcdm`](vignettes/overview-simcdm.html)
- [Using `simcdm` in R packages](vignettes/simcdm-in-packages.html)

## Authors

James Joseph Balamuta and Steven Andrew Culpepper
with contributions from Aaron Hudson.

## Citing the `simcdm` package

To ensure future development of the package, please cite `simcdm` package if 
used during the analysis or simulations. Citation information for the package
may be acquired by using in _R_:

```{r, eval = FALSE}
citation("simcdm")
```

## License

GPL (>= 2)
